\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-18 methodology.tex
some updates in section 4

\item[RepairMonitor] collects states from all \texttt{ExtentNode} machines in the testing harness and verifies desired properties, such as that an extent is replicated or repaired at the expected ENs.
\end{description}

@@

The \texttt{RepairMonitor} machine transitions between a cold state and a hot state. Whenever an extent node fails, \texttt{RepairMonitor} is notified. As soon as the number of extent replicas falls below a specified target, \texttt{RepairMonitor} transitions into the hot \emph{repairing} state, where the missing replica is being repaired. Whenever a replica is repaired, the \texttt{RepairMonitor} machine is also notified. It transitions into the cold \emph{repaired} state, when the replica number reaches the target again, as illustrated in Figure~\ref{fig:monitor}.

%It verifies the property that the number of extent replica {\em eventually} reaches the target.

In the extent repair testing scenarios, \texttt{RepairMonitor} verifies that it should {\em always eventually} end up in the cold repaired state. Otherwise, the \texttt{RepairMonitor} machine is stuck in the hot repairing state for {\em infinitely} long. This indicates that the corresponding execution sequence results in an extent replica never being repaired, which is a liveness bug!

\begin{figure}[t]
\begin{lstlisting}
class RepairMonitor : Machine {
  // true: EN has replica, false: EN has no replica
  private Dictionary<Machine, bool> ExtentNode2Replica;

@@

The culprit is in $iv)$, where \texttt{ExtMgr} receives a sync report from EN$_0$ after deleting the EN. This may occur in \psharp because of arbitrary message interleaving. It may also occur, albeit much less frequently, in the stress testing due to messages being delayed in the network. This explains why the bug only occurs from time to time in the stress testing and also takes long execution to trigger. In contrast, \psharp allows the bug to manifest quickly, the developers to iterate rapidly, the culprit identified promptly, and the fix solution verified effectively, all of which should vastly increase the productivity of distributed storage system development.

>>>>

\item[RepairMonitor] collects states from all \texttt{ExtentNode} machines in the testing harness and checks desired properties, such as that an extent is replicated or repaired at the expected ENs.
\end{description}

@@

\texttt{RepairMonitor} is a monitor machine (see Section~\ref{sec:bg:bugs}) that transitions between a cold state and a hot state. Whenever an extent node fails, \texttt{RepairMonitor} is notified. As soon as the number of extent replicas falls below a specified target, \texttt{RepairMonitor} transitions into the hot \emph{repairing} state, where the missing replica is being repaired. Whenever a replica is repaired, the \texttt{RepairMonitor} machine is also notified. It transitions into the cold \emph{repaired} state, when the replica number reaches the target again, as illustrated in Figure~\ref{fig:monitor}.

%It checks the property that the number of extent replica {\em eventually} reaches the target.

In the extent repair testing scenarios, \texttt{RepairMonitor} checks that it should {\em always eventually} end up in the cold repaired state. Otherwise, the \texttt{RepairMonitor} machine is stuck in the hot repairing state for {\em infinitely} long. This indicates that the corresponding execution sequence results in an extent replica never being repaired, which is a liveness bug!

\begin{figure}[t]
\begin{lstlisting}
class RepairMonitor : Monitor {
  // true: EN has replica, false: EN has no replica
  private Dictionary<Machine, bool> ExtentNode2Replica;

@@

The culprit is in $iv)$, where \texttt{ExtMgr} receives a sync report from EN$_0$ after deleting the EN. This may occur in \psharp because of arbitrary message interleaving. It may also occur, albeit much less frequently, in the stress testing due to messages being delayed in the network. This explains why the bug only occurs from time to time in the stress testing and also takes long execution to trigger. In contrast, \psharp allows the bug to manifest quickly, the developers to iterate rapidly, the culprit identified promptly, and the fix solution tested effectively and thoroughly, all of which should vastly increase the productivity of distributed storage system development.
